Legends for supplementary material

### 2019-02-27 Manuscript/Supplementary/supplementary_legends.Rmd
Results review
commented out legends
edditted legend

**Supplementary Table 4. Hi-C Data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains and where they can be downloaded.

@@

**Supplementary Figure 1-8. Distance Densities across cell lines and resolutions.**
Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for GM12878 (left column) and K562 (right column) cell lines. The untransformed distances (red) are highly right skewed. After performing a $log_{2}$ tranformation (blue), the distances exhibited more normalized densities.

@@

**Supplementary Figures 9-23. Precision-Recall curves for 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique. GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).

**Supplementary Table 2. Area under Precision-Recall Curves.** Comparison of models applied to different data resolutions, resampling techniques, and predictor types for each of the two cell lines in terms of AUPRC. The column labeled "All" denotes models with all 3 combined predictor types.

**Figure 3. Recursive Feature Elimination for 25 kb, 50 kb, and 100 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 25 kb, 50 kb, and 100 kb resolution data were recursively evaluated at different subsets of feature size. For convenience and computational efficiency, feature size decreasing in powers of 2 was considered. The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1. Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).

>>>>

**Supplementary Table 4. Hi-C Data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.

@@

**Supplementary Figure 1. Distance Densities across cell lines and resolutions.**
Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines. The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.

@@

<!--
**Supplementary Figures 9-23. Precision-Recall curves for 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique. GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red). 
-->

<!--
**Supplementary Table 2. Area under Precision-Recall Curves.** Comparison of models applied to different data resolutions, resampling techniques, and predictor types for each of the two cell lines in terms of AUPRC. The column labeled "All" denotes models with all 3 combined predictor types.
-->

<!--
**Figure 3. Recursive Feature Elimination for 25 kb, 50 kb, and 100 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 25 kb, 50 kb, and 100 kb resolution data were recursively evaluated at different subsets of feature size. For convenience and computational efficiency, feature size decreasing in powers of 2 was considered. The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1. Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).
-->
